---
title: "Finanças e Programação"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```



# Curso Formação Aplicada em Finanças e Programação

## Introdução a Programação usando R

### 1) Conhecendo a Linguagem de Programação R

### 2) Tipos básicos de dados no R

### 2) Atribuição de variável

### 2) Aritmética

*Você pode usar o R para fazer alguns cálculos*

`Adição (+)`

### Exercício: Faça a adição de dois números:
```{r adicao, exercise=TRUE}

```
`Subtração (-)`

### Exercício: Faça a subtração de dois números:
```{r subtracao, exercise=TRUE}

```
`Divisão (/)`

### Exercício: Faça a divisão de dois números:
```{r divisao, exercise=TRUE}

```
`Divisão inteiro (%/%)`

### Exercício: Faça a divisão de dois números inteiros (entre os números use o seguinte sinal `%/%`:
```{r div_inteiro, exercise=TRUE}

```


### 1) Usando como calculadora

*Você pode usar o ambiente de código logo abaixo para fazer cálculos. Experimente calcular 2 + 2 e clique no botão logo ao lado direito superior "Run Code"*

```{r calculadora, exercise=TRUE}

```


### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Matemática Financeira

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

## Introdução a Programação usando R2

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r three-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

## Economia

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

## Capital de Giro

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

```2 + 2```
```+```


